---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cdgd

[![R-CMD-check](https://github.com/ang-yu/cdgd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ang-yu/cdgd/actions/workflows/R-CMD-check.yaml)
![CRAN Downloads overall](https://cranlogs.r-pkg.org/badges/grand-total/cdgd)


The package cdgd implements the causal decompositions of group disparities in [Yu and Elwert (2025)](https://projecteuclid.org/journals/annals-of-applied-statistics/volume-19/issue-1/Nonparametric-causal-decomposition-of-group-disparities/10.1214/24-AOAS1990.full).

## Installation

The latest release of the package can be installed through CRAN.

```R
install.packages("cdgd")
```

The current development version can be installed from source using devtools.

```R
devtools::install_github("ang-yu/cdgd")
```

## Examples 
  
```{r example}
library(cdgd)  

# load the simulated example data
data(exp_data)
head(exp_data)
```

### Use cdgd0_ml, cdgd0_pa, or cdgd0_manual for unconditional decomposition

```{r unconditional}
results0 <- cdgd0_pa(Y="outcome",D="treatment",G="group_a",X=c("confounder","Q"),data=exp_data,alpha=0.05)

round(results0$results, 4)
```

### Use cdgd1_ml, cdgd1_pa, or cdgd1_manual for conditional decomposition 

```{r conditional}
results1 <- cdgd1_pa(Y="outcome",D="treatment",G="group_a",X="confounder",Q="Q",data=exp_data,alpha=0.05)

round(results1, 4)
```
